Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-12 arxiv/tools.tex
revise

 Moreover, we can obtain the following concentration estimates for random noise in the setting of Section \ref{sec_same}.

 \begin{corollary}\label{cor_calE}
Suppose the entries of $\cal E=[\epsilon^{(1)},\epsilon^{(2)},\cdots, \epsilon^{(t)}]\in \R^{n\times t}$ are i.i.d. random variables of mean zero, variance $\sigma^2$ and bounded moments up to any order. Then we have that

 using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that all moments of $\varepsilon_i$ exist by Assumption \eqref{assmAhigh2}
 \end{corollary}

>>>>

Next we can obtain the following concentration estimates for random noise in the setting of Section \ref{sec_same}.

 \begin{corollary}\label{cor_calE}
Suppose the entries of $\cal E=[\epsilon^{(1)},\epsilon^{(2)},\cdots, \epsilon^{(t)}]\in \R^{n\times t}$ are i.i.d. random variables of mean zero, variance $\sigma^2$ and bounded moments up to any order. Then for any deterministic vector $v\in \R^n$ and deterministic $n\times n$ matrix $B\in \R^{n\times n}$, we have that with high probability,
\be\label{vcalE} |v^\top \epsilon^{(i)}| \le \sigma n^{c} \|v\|, \ee
and
\be\label{vcalA2} \left|(\epsilon^{(i)})^\top B \epsilon^{(j)} - \delta_{ij}\cdot \sigma^2 \tr(B)\right| \le n^{c} \|B\|_F ,\ee
for any small constant $c>0$. As a consequence, equations \eqref{vcalE} and \eqref{vcalA2} imply that 
\be\label{vcalAE3}
\|v^\top \cal E\| \le \sigma n^{c} \|v\|, \ \ \ \text{and}\ \ \ \left\| \cal E^\top B \cal E - \sigma^2 \tr(B)\cdot \id_{t\times t}\right\|_F \le n^{c} \|B\|_F ,
\ee
 with high probability for any small constant $c>0$.
 \end{corollary}
 \begin{proof}

 \end{proof}
